\documentclass{my_cv}
\usepackage[skins]{tcolorbox}
\usepackage[hidelinks]{hyperref}

\begin{document}
\begin{multicols}{2}[
    \titletext{Harvey}%
        {Fretwell}%
        {Software Engineer}%
        {\href{mailto:hgfretwell@gmail.com}{hgfretwell@gmail.com}}%
        {\href{tel:447377693636}{+44 7377 693636}}%
        {\href{https://github.com/harveyf2801}{harveyf2801}}%
        {\href{https://www.linkedin.com/in/harveyfretwell/}{linkedin.com/in/harveyfretwell/}}%
        {\href{https://harveyf2801.github.io/portfolio/}{harveyf2801.github.io/portfolio/}}%
]
\end{multicols}

\section{\faFileText}{SUMMARY}
As a soon-to-be sound engineering graduate with experience in the audio software industry, I bring strong problem-solving skills, a collaborative mindset, and a diverse technical skill set. Organised, detail-oriented, and self-motivated, I am eager to apply and expand my expertise in a dynamic software engineering role, contributing to impactful projects and advancing my professional growth.

\begin{multicols}{2}
\section{\faPencil}{WORK EXPERIENCE}

\work{Demonstrator / Mar 2019 - May 2020}%
    {Birmingham City University - Birmingham, UK}%
    {Bringing hands-on expertise, specifically teaching audio software development including C++ and the JUCE framework to university students.}%
    {C++, Git, JUCE, Computer Science}
    
\work{QA Engineer / Aug 2022 - Aug 2023}%
    {Audient - Hampshire, UK}%
    {Developed and implemented a comprehensive CI/CD solution using Python, automating - unit, integration, and end-to-end tests for all products. I also contributed to various roles, such as software development, supporting repairs, and streamlining bug reporting processes for enhanced efficiency.}
    {Python, C++, JUCE, GitFlow, DSP}
    
\section{\faList}{SKILLS}

\textbf{Languages:} C++, Python, MATLAB, JS, HTML, CSS,

\noindent\textbf{Tools:} PyTorch, Tensorflow, PyTest, JUCE, Jekyll

\noindent\textbf{Other:} CI/CD, Gitflow, GUI Design, Data Science and ML, DSP, Networking

\section{\faGraduationCap}{EDUCATION}
    
\school{BSc Sound Engineering / 1:1 / Sept 2020 - July 2024} %
{Birmingham City University - Birmingham, UK} %
{\textbf{{Thesis}}: Comparative analysis of auto phase alignment techniques: traditional DSP methods VS. neural network approaches.}
    
\school{A-Levels / AAB / Sept 2018 - July 2020} %
{King Edward VI College - Nuneaton, UK} %
{Computer Science: A
| Music Technology: A
| Music: B}

\section{\faPaintBrush}{OTHER PROJECTS}
\begin{itemize}[noitemsep]
    \item Created instrument classification models comparing SVM, KNN, and Random Subspace Ensemble, utilising Python, PyTorch, and MATLAB.
    \item Implemented a Deep Neural Network in PyTorch for phase aligning two audio sources.
    \item Developed audio effects like compressors and EQs, as well as standalone applications using C++ and JUCE.
    \item Designed a 2-story multi-purpose recording studio with full acoustic treatment. Additionally, crafted applications to calculate reverberance and assess noise pollution.
    \item Engineered polyphonic synthesisers with Arduino and DaisySP, using C++.
    \item Created a cross-platform automation library in Python using accessibility tags to perform end-to-end testing of applications.
    \item Built a custom portfolio website using HTML, CSS, JavaScript, and Jekyll.
\end{itemize}

\section{\faStar}{AWARDS}

\begin{itemize}[noitemsep]
    \item Grade 6 on both classical guitar and keyboard, and performed as lead trombone in Enderby Brass Band at various concerts and contests around Europe.
    \item Dante Level 1, 2 and 3.
    \item Duke of Edinburgh bronze and silver award.
    \item National Citizen Service award.
\end{itemize}

\section{\faSoccerBallO}{ACTIVITIES / INTERESTS}

\begin{itemize}[noitemsep]
    \item Founded and managed the Live Sound Society at university, training new members and organised events including festivals, karaoke nights, and weekly concerts.
    \item Volunteered as leader at local scout group, planning and running diverse activities like first aid, survival skills, nights out, and camping trips, fostering leadership and communication skills.
    \item Volunteered as an instructor in the local brass band's trombone section; aiding other players in junior band, offering guidance to advance them to youth band.
\end{itemize}

\end{multicols}

\begin{center}
References available on request
\end{center}
\end{document}
